\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[margin=2cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{parskip}
\usepackage{setspace}

% Colors (matching CV)
\definecolor{primary}{RGB}{30, 64, 175}
\definecolor{secondary}{RGB}{71, 85, 105}
\definecolor{accent}{RGB}{37, 99, 235}

% Links
\hypersetup{
    colorlinks=true,
    linkcolor=accent,
    urlcolor=accent
}

% No page numbers
\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\Huge\bfseries\color{primary} Bilal KEFIF}\\[5pt]
    {\large\color{secondary} Software Engineering Student}\\[10pt]
    \faMapMarker*\ Paris, France \quad
    \faPhone\ +33 6 22 39 22 30 \quad
    \faEnvelope\ \href{mailto:bilalkefif243@gmail.com}{bilalkefif243@gmail.com}\\[5pt]
    \faLinkedin\ \href{https://www.linkedin.com/in/bilal-kefif-94400015a}{linkedin.com/in/bilal-kefif-94400015a} \quad
    \faGlobe\ \href{https://portfoliobilalkefif.netlify.app?lang=en}{portfoliobilalkefif.netlify.app?lang=en}
\end{center}

\vspace{1cm}

\begin{flushright}
    To the Hiring Manager\\
    \today
\end{flushright}

\vspace{0.5cm}

\textbf{Subject: Application for a 3-4 Month Internship in Cybersecurity / Software Development}

\vspace{0.5cm}

Dear Sir/Madam,

I am currently a second-year student (Master's level) at \textbf{ENSIIE} (National School of Computer Science for Industry and Business), specializing in software engineering. As part of my academic program, I will soon undertake an exchange semester at \textbf{Université Laval} (Quebec) focused specifically on \textbf{cybersecurity}. I am seeking a 3-4 month internship starting in June 2026 to apply my technical skills and passion for system security.

My academic background has provided me with a solid foundation in development (C, Java, Python) and fundamental security concepts (formal methods, software verification). My semester at Université Laval will strengthen these skills with advanced modules such as software security, IoT security, and blockchain technology. I am particularly interested in the opportunity to apply this theoretical knowledge to real-world security or complex development challenges within your organization.

During my previous internship at \textbf{idIA Tech}, I developed professional rigor and deep analytical capabilities. I notably practiced process automation, tasks requiring a thorough understanding of web application functionality and network protocols. I also contributed to restoring an IDE debugger, demonstrating my ability to discover and analyze complex existing code to correct and optimize it.

Versatile and curious, I have worked on various technical projects, ranging from web application development (React/Flask) to systems programming (card game in C, text editor in OCaml). This diversity of experiences demonstrates my ability to quickly adapt to new technologies and environments.
Aware that my student background may present gaps when facing professional requirements, I actively compensate through continuous self-training. I regularly train via specialized platforms such as TryHackMe and participate in additional cybersecurity training courses. I am truly determined to leverage this deep passion for these fields.

Dynamic and motivated, I would be delighted to join your team to contribute to your projects while continuing my learning journey. I am available at your convenience for an interview to discuss my motivation in greater detail.

Thank you for considering my application. I look forward to hearing from you.

\vspace{1cm}

\begin{flushright}
    Sincerely,\\[0.5cm]
    \textbf{Bilal KEFIF}
\end{flushright}

\end{document}
